\LARGE \bf A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself

### 2014-11-27 main.tex
R1 'necessary letter models' statement

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities was sought
which is capable of generating the necessary letter models. Depending on the parameters input to
the letter models, different quality shapes should be generated. The system can
therefore be configured to improve its writing by modifying the parameters used
to generate the letters, based on feedback from the reinforcement learning
partner. To this end, a method which can generate a model from real-world data
has been employed in order to capture realistic variations in letters.

@@

\subsection{Responding to Feedback}

>>>>

For the development of a learning algorithm in the context of
handwriting, a parameterisation of letters and their deformities was sought such 
that different quality shapes can be generated, depending on the parameters input to
the letter models. This allows the system to be configured to improve its writing 
by modifying the parameters used to generate the letters, based on feedback from the 
reinforcement learning partner as addressed in Section \ref{sec:learningAlg}. 
%To this end, a method which can generate a model from real-world data
%has been employed in order to capture realistic variations in letters.

@@

\subsection{Responding to Feedback}\label{sec:learningAlg}
